\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[modulo]{lineno}
\usepackage[numbers]{natbib}
\usepackage{url}
\usepackage{import}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}

\input{extra_macros/macro_editing}
\input{extra_macros/macro_tables}
\input{extra_macros/macro_interviews}

\title{Quality Requirements in Agile as a Knowledge Management Problem: More than Just-in-Time%\\ \Large{--Position Paper--}
}

\author{
\IEEEauthorblockN{Eric Knauss, Grischa Liebel}
\IEEEauthorblockA{Computer Science and Engineering\\
Chalmers $\mid$ University of Gothenburg \\ Gothenburg, Sweden \\ \{knauss,grischa\}@chalmers.se }
\and
\IEEEauthorblockN{Kurt Schneider}
\IEEEauthorblockA{Software Engineering Group\\
Leibniz Universit\"at Hannover \\ Hannover, Germany \\ ks@inf.uni-hannover.de}}

\begin{document}
\maketitle

\begin{abstract}
%\eric{very drafty, to set the scene}
Just-in-time (JIT) approaches have been suggested for managing non-functional requirements in agile projects.
However, many non-functional requirements cannot be raised and met on the spot. 
In this position paper, we argue that effective JIT engineering of quality requirements depends on a solid foundation of long-term knowledge  about all relevant quality requirements.
We present two examples from projects related to safety and security and show that not all aspects of these quality requirements can be invented and changed just in time. 
% Different roles and different stakeholders are responsible, and the tasks at hand determine how they can be handled. 
Further, managing for example operationalization of quality requirements just in time depends on sufficient understanding of (i) customer value and (ii) the system under construction that must be shared by the engineering team.
%
%Thus, it is not sufficient to focus on JIT requirements engineering alone. 
If a Learning Software Organization (LSO) intends to increase agility and speed up system development, it needs a holistic concept for managing this knowledge. 
%The assumed co-existence of JIT and solid non-functional requirements needs a structure for eliciting, storing, and managing quality requirements. 
%We claim that JIT management of quality requirements must be complemented by a long-term perspective.
We propose that a knowledge-management framework can facilitates JIT-RE by structuring, representing, and allowing updates of long-term knowledge about quality requirements.
Such a knowledge-management framework should allow to map user value to system requirements and have important properties to allow JIT RE and sustainable evolution. 
%We discuss properties of , by allow providing knowledge management structures and counterparts to represent – and update – the knowledge aspect of non-functional requirements.      \kurt{Which properties of the framework are important so that it supports JIT and sustainable evolution?}

\end{abstract}

\begin{IEEEkeywords}
just-in-time RE, quality requirements, managing requirements knowledge
\end{IEEEkeywords}

\input{files/introduction}
\input{files/literature}
\input{files/safety-example}
\input{files/security-example}
\input{files/km-framework}
\input{files/conclusions}

\textbf{Acknowledgments.}
This work was supported by  Software Center (RE for Large-Scale Agile System Dev. Project) and German DFG Priority Programme 1593 (Design for Future).

\bibliographystyle{plainnat}
\bibliography{jit-as-km-problem.bib}
\end{document}